---
title: "Adv Data Mining and Analytics - Assignment 1"
author: "msasnur@kent.edu"
date: "28/02/2020"
output:
  html_document: default
  pdf_document: default
---

Initializing all the required libraries.

```{r}
library(ISLR)
library(dplyr)
library(ggplot2)
library(gridExtra)
```

Assigning Carseats Dataset to safeBabies Variable by selecting only Sales, Price, and Shelf Location columns.

```{r}
safeBabies <- Carseats %>% select("Sales", "Price", "ShelveLoc")
```

Splitting dataset into three parts based on Shelf Location

```{r}
good <- filter(safeBabies,ShelveLoc == 'Good')
medium <- filter(safeBabies,ShelveLoc == 'Medium')
bad <- filter(safeBabies,ShelveLoc == 'Bad')
```

Question 1:

Building Linear Regression model between Sales(dependent) and Price(independent) for Good Shelf Location.

```{r}
good_ordered <- good[order(good$Price),]
model_1 <- lm(Sales ~ Price, data = good_ordered)
summary(model_1)
```

Finding out optimal price for Good Shelf Location by subsituting values obtained from above regression model in the following equation. 

```{r}
good_optimal_price = (-0.065785 *55 - 17.968864)/(2 * -0.065785)
print(good_optimal_price)
```

Varying production cost from $40 to $85, to find optimal price 

```{r}
result <- vector("numeric", 40)
for(cost in 40:86) {
  good_optimized_result <- (-0.065785 *cost - 17.968864)/(2 * -0.065785)
  result[cost - 40] <- good_optimized_result
}
```

Using cbind to create dataframe by binding Optimized price and change in cost. Naming the columns accordingly.

```{r}
price<- c(40:85)
good_optimized_price<-cbind.data.frame(result,price)
names(good_optimized_price)<-c('Optimized_Price','Change_in_Cost')
```

Question 2

Similar to above solution for 1st question. Repeating all the codes for Bad Shelf Location to find optimal price. 

```{r}
bad_ordered<-bad[order(bad$Price),]
model_2 <- lm(Sales ~ Price, data = bad_ordered)
summary(model_2)

bad_optimal_price = (-0.05522 * 55 - 11.832984) / (2 * -0.05522)
print(bad_optimal_price)

result_1 <- vector("numeric", 40)
for(cost in 40:86) {
  bad_optimized_result <- (-0.05522 *cost - 11.832984)/(2 * -0.05522)
  result_1[cost - 40] <- bad_optimized_result
}

bad_optimized_price<-cbind.data.frame(result_1,price)
names(bad_optimized_price)<-c('Optimized_Price','Change_in_Cost')
```

Plotting above two results and comparing them to see the variations in optimal price using ggplot

```{r}
plot_good <- ggplot(good_optimized_price, aes(Optimized_Price, Change_in_Cost, colour='Good location')) +
             labs(title = 'Optimized Price varying with cost',x='Optimized Price',y='Cost') +
             geom_line() +
             scale_color_manual("", values = ("Good Price" = "red")) +
             geom_point(colour='black')

plot_bad <- ggplot(bad_optimized_price, aes(Optimized_Price, Change_in_Cost, colour='Bad location')) +
            labs(x='Optimized price',y='Cost') +
            geom_line() +
            scale_color_manual("", values = ("Bad Price" = "blue")) +
            geom_point(colour='black')
```

Using GridExtra library to display the plots together.

```{r}
grid.arrange(plot_good, plot_bad, ncol=1)
```

We have obtained optimal price to sell carseats when production cost is $55 
- for good shelf location as 164.07
- for bad shelf location as 134.64

Looking at the graph we can observe that optimal price varies from $120 to $150 for Bad shelf location and from $150 to $180 for good shelf location when we vary production cost from $40 to $85